Hydras, Ordinals \& Co.\\ A library in Coq of entertaining formal mathematics

### 2021-10-22 doc/gaia-chapter.tex
Add symmetric notations for hydras/gaia. Fix a few typos
more snippets in gaia-chapter

@@

\subsubsection{A few constants}

\inputsnippets{T1Bridge/constantRefs}

>>>>

Most used constants and functions will also get standardized
non-ambiguous names.

\inputsnippets{T1Bridge/MoreNotations}

@@

\subsubsection{A few constants}
For each constant: $0$, $1$, \dots, $n$ and $\omega$ we prove
that the \texttt{hydras}' definition refines \texttt{gaia}'s.
\inputsnippets{T1Bridge/constantRefs}

\subsubsection{Unary functions}

\inputsnippets{T1Bridge/unaryRefs}

\subsubsection{Binary operations}
The binary operations $+$ and $\times$ are defined the same way in both libraries. Please note that they require comparison of ordinal terms. So, the proof of the following lemmas applies
compatibility lemmas like \texttt{compare\_ref} (see Section~\vref{sect:gaia-compare-ref}).

\inputsnippets{T1Bridge/plusRef, T1Bridge/multRef}

\subsection{Order and comparison}

\label{sect:gaia-compare-ref}
\inputsnippets{T1Bridge/compareRef}

\inputsnippets{T1Bridge/ltRef}
